ODGI: understanding pangenome graphs

### 2021-11-01 manuscript/main.tex
spoiler

\address{
$^{\text{\sf 1}}$University of Tor Vergata, Rome, Italy \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 3}}$University of Tennessee Health Science Center, Memphis, TN, USA
}

>>>>

\address{
$^{\text{\sf 1}}$Human Technopole, Milan, Italy \\
$^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of T\"ubingen, T\"ubingen, Germany, 72076 \\
$^{\text{\sf 3}}$University of Tennessee Health Science Center, Memphis, TN, USA
}
